%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Logan Sherwin} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\ 724-771-3142 $|$ \href{mailto:lsherwin10@gmail.com}{\raisebox{-0.2\height}\  \underline{lsherwin10@gmail.com}} $|$ 
    \href{https://linkedin.com/in/logan-sherwin/}{\raisebox{-0.2\height}\ \underline{linkedin.com/in/logan-sherwin}}  $|$
    \href{https://github.com/lsherwin10}{\raisebox{-0.2\height}\ \underline{github.com/lsherwin10}} $|$ \href{https://logansherwin.com/}{\raisebox{-0.2\height}\ \underline{logansherwin.com}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Chicago}{Sep. 2019 -- Jun. 2023}
    %   {M.S. in Computer Science $\mid$ B.S. in Computer Science, Machine Learning Specialization}{Chicago, IL}
      {Joint B.S./M.S. in Computer Science, Machine Learning Specialization}{Chicago, IL}
  \resumeSubHeadingListEnd
  \vspace{-6pt} \small GPA: 3.82/4.00 \\
  \vspace{-1pt} \small Honors: 2021-22 Dean's List \vspace{-8pt}

%------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{5}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Algorithms
%                 \item Comp Architecture
%                 \item Computer Security
%                 \item Computer Vision
%                 \item Databases
%                 \item Ethics \& Privacy
%                 \item HCI
%                 \item Machine Learning
%                 \item Networks
%                 \item Robotics
                
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Amazon}{Sep. 2023 -- Present}
      {Software Development Engineer -- Private Brands Discovery}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Contributed to dozens of projects to support our customers' discovery of Amazon Private Brands \href{https://www.amazon.com/stores/node/20648519011?channel=discovbar?field-lbr_brands_browse-bin=AmazonBasics&ref_=nav_cs_amazonbasics}{\underline{products}}}
        \resumeItem{Served appropriate substitute recommendations to customers on product detail pages}
        \resumeItem{Improved dataset generation pipelines to improve its efficiency and increase relevance of product recommendations}
        \resumeItem{Faciliated multiple compliance and migration projects involving various internal and AWS services}
        \resumeItem{Mentored a Software Development Engineer Intern throughout Summer 2024, supported his growth and learning in the industry, and guided him to complete his project and subsequently receive a full-time job offer}
      \resumeItemListEnd
  
  \resumeSubheading
      {Amazon}{Jun. 2022 -- Sep. 2022}
      {Software Development Engineer Intern}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Implemented a new core operator for an internal service for customers to access AWS SageMaker inference endpoints}
        \resumeItem{Handled customer requests passing through the platform by building and executing requests from our service to the AWS SageMaker endpoint through a non-blocking IO system written in Java}
        \resumeItem{Processed response data from the endpoint and converted it to the platform's query language as output}
        \resumeItem{Allowed customers to implement calls to SageMaker models for inference in their business logic}
      \resumeItemListEnd

    \resumeSubheading
      {SESCO Enterprises, LLC}{Jun. 2021 -- Sep. 2021}
      {Quantitative Developer Intern}{Chicago, IL}
      \resumeItemListStart
        \resumeItem{Developed a simulation engine to estimate the fair values of Financial Transmission Rights, an auctioned options and obligations market for wholesale electricity}
        \resumeItem{Centered around analyzing the behavior of market participants for correlated auctions and assets}
        \resumeItem{Implemented backtesting for the model, accounting for price elasticity}
        \resumeItem{Written in Python, with extensions in Nim for optimizing the program's numerical algorithms}
      \resumeItemListEnd

    \resumeSubheading
      {University of Chicago -- Department of Computer Science}{Mar. 2021 -- Jun. 2021}
      {Teaching Assistant}{Chicago, IL}
      \resumeItemListStart
        \resumeItem{Guided over 100 student’s learning in an introductory computer science course by leading lab sessions and solving problems that arose in their code}
        \resumeItem{Held office hours to support students in their learning and provide feedback on their code}
        \resumeItem{Assessed student performance on graded assignments as a member of a ten-person staff team}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Adrenaline Recruiting}{}}{Feb. 2023 -- Aug. 2024}
      \resumeItemListStart
        \resumeItem{Developed an iOS app alongside my college teammate to help high-school divers display their skills to college recruiters}
        \resumeItem{Reached out to diving coaches to understand their needs when recruiting athletes to join their varsity teams}
        \resumeItem{Integrated with DiveMeets.com to compute proprietary statistics and metrics for athletes}
        \resumeItem{Functioned as the lead engineer on the project, ensuring high-quality contributions across all engineers}
      \resumeItemListEnd
      \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Diving Pose Estimation}{}}{Aug. 2022 -- Sep. 2022}
          \resumeItemListStart
            \resumeItem{Implemented pose estimation using the OpenCV Python package to identify joints and compute joint angles of a diver}
            \resumeItem{Overlayed joint angles at a given video frame to show the angles at a given moment during the dive}
            \resumeItem{Wrote new sequence of frames with angle and pose overlays to disk for divers to observe after analysis}
          \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{Schedule Generator}{}}{Jun. 2021 -- Aug. 2021}
      %     \resumeItemListStart
      %       \resumeItem{Implemented an interval scheduling algorithm in Python to determine the best arrangement of employees by week} 
      %       \resumeItem{Considered availability of workers and prioritized shift distribution based on seniority}
      %     \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages: }{Python, Java, Scala, TypeScript, SQL, C++, Swift, Nim} \\
     \textbf{Technologies/Frameworks: }{AWS, SciPy Stack, Git, MongoDB, PostgreSQL} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Extracurriculars}
    \resumeSubHeadingListStart
        \resumeSubheading{Alpha Kappa Psi Business Fraternity}{Jan. 2022 -- Jun. 2023}{}{} \vspace{-13.5pt}
        \resumeSubheading{College Varsity Swimming and Diving Team -- Captain}{Oct. 2019 -- Jun. 2023}{}{}
    \resumeSubHeadingListEnd


\end{document}
